MixEth: efficient trustless coin mixing service for Ethereum

### 2018-10-15 article/main.tex
Typos fixed in article

\textbf{Note: this is an early-stage work-in-progress! Security proofs, implementation and many more are yet to come!} 
\begin{abstract}
Cryptocurrencies enable users to transact with each other without relying on trusted parties or intermediaries. These transactions are recorded in an immutable, publicly verifiable ledger. Due to this transparent nature of the ledger, privacy is notably reduced. If the link between users' public key and their physical identity is exposed  their pseudonymity is lost. One way to increase users' privacy is to deploy coin mixing services. In this paper, we present MixEth, which is a trustless coin mixing service. MixEth is more efficient than any proposed trustless coin tumbler. It requires only $3$ on-chain transactions at most per user and $1$ off-chain. It achieves strong notions of anonimity and is able to resist denial-of-service attacks.      
\end{abstract}
\keywords{Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer}

@@

\section{Background}
\subsection{Notations}
In most cases if it is possible we will stick to the notations used in \cite{meiklejohn2018mobius} for sake of uniformity. 
Let $[]$ denote the empty tuple. For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$. The cardinality of a finite set $X$ is denoted as $|X|$. In the following let $\lambda \in \mathbb{N}$ the security parameter and its unary representation is $1^{\lambda}$. If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$. The symmetric group of degree $n$ is written as ${S}_n$. In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation. Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript. Let $PK$ denote the set of public keys belonging to receivers.

@@

$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B)$: after the end of the shuffling period users are allowed to withdraw their funds. Note that here the transaction will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather final shuffling accumulated constant.

@@

\subsection{Withdrawing}
Let $C^*$be the final shuffling accumulated constant. For a recipient whose public key $sG \in initPubKeys[]$, in the final shuffle there will be $sC^*$. The recipient can prove to MixEth that she knows $s$ by using a modified ECDSA, which uses $C^*$ as the generator element instead of the standardized $G$.
\subsection{MixEth pseudocode}

>>>>

\textbf{Note: this is an early-stage work-in-progress! Security proofs, implementation and many more are yet to come!} 
\begin{abstract}
Cryptocurrencies enable users to transact with each other without relying on trusted parties or intermediaries. These transactions are recorded in an immutable, publicly verifiable ledger. Due to this transparent nature of the ledger, privacy is notably reduced. If the link between users' public key and their physical identity is exposed  their pseudonymity is lost. One way to increase users' privacy is to deploy coin mixing services. In this paper, we present MixEth, which is a trustless coin mixing service. MixEth is more efficient than any proposed trustless coin tumbler. It requires only $3$ on-chain transactions at most per user and $1$ off-chain. It achieves strong notions of anonymity and is able to resist denial-of-service attacks.      
\end{abstract}
\keywords{Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer}

@@

\section{Background}
\subsection{Notations}
In most cases if it is possible we will stick to the notations used in \cite{meiklejohn2018mobius} for sake of uniformity. 
Let $[]$ denote the empty tuple. For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$. The cardinality of a finite set $X$ is denoted as $|X|$. In the following let $\lambda \in \mathbb{N}$ be the security parameter and its unary representation is $1^{\lambda}$. If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$. The symmetric group of degree $n$ is written as ${S}_n$. In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation. Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript. Let $PK$ denote the set of public keys belonging to receivers.

@@

$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B)$: after the end of the shuffling period users are allowed to withdraw their funds. Note that here the transaction will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather the final shuffling accumulated constant.

@@

\subsection{Withdrawing}
Let $C^*$ be the final shuffling accumulated constant. For a recipient whose public key $sG \in initPubKeys[]$, in the final shuffle there will be $sC^*$. The recipient can prove to MixEth that she knows $s$ by using a modified ECDSA, which uses $C^*$ as the generator element instead of the standardized $G$.
\subsection{MixEth pseudocode}
